Constructing the transition graphs of interacting hysterons

### 2022-06-28 Paper_draft.tex
Expanded part on main loops within piece on hysteron ordering

We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value. As a result, there can only be as many graphs as there are permutations of the order of switching fields. In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$. In addition, because we never compare an up switching field with a down switching fields, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$. The number of orderings that can lead to a unique graph is then $N!\times N!$. When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$. Indeed, we have that there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different main loop.\\ 
When hysterons are allowed to interact, however, the situation changes. On one hand, there are then $2(2^N-1)$ states $U_i^{+, -}(S)$, and because of the possibility of avalanches, the ordering between all of the states must be considered. On the other hand, the state transition graph is only determined by a partial order between some of the switching fields. As a result, the number of permutations greatly outnumbers the number of unique state transition graphs. For $N=2$, the number of permutations is $8! = 40320$ while we know the number of graphs to be 13. For $N=3$, the number of permutations is as high as $24! \approx 6\times 10^{23}$.\\
We conclude that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields. Even so, we can make use of the fact that the state transition graph only depends on a partial ordering of the switching fields. Namely, we know that each graph has an underlying set of linear inequalities $U_i(S_A) > U_j(S_B)$, which we refer to as the design inequalities\cite{vhecke2021}. The solution space of the design inequalities provides the region in parameter space that leads to the given graph. In particular, if the design inequalities have no solution, then the given graph is not realizable.\\

>>>>

We observe that in essence, it is only the ordering of the switching fields ${U_i^{+, -}(S)}$ that determines the state transition graph, rather than their absolute value. As a result, there can only be as many graphs as there are permutations of the order of switching fields. In the case where hysterons are non-interacting, there are only $2N$ switching fields $\{u_i^{+, -}\}$. In addition, because we never compare an up switching field with a down switching fields, the only orderings that can change the graph are the partial orderings of the up switching fields $\{u_i^+\}$ and of the down switching fields $\{u_i^-\}$. The number of orderings that can lead to a unique graph is then $N!\times N!$. When we fix the up switching fields to account for exchange symmetry, we find that the number of permutations is only $N!$.\\
Indeed there are $N!$ Preisach graphs for a collection of $N$ hysterons, each corresponding to a different ordering of the down switching fields. The ordering for each graph can be easily identified by considering the main loop: that is, the sequence of down transitions connecting the state with all $s_i = 1$ to that with all $s_i=0$. We accordingly use the main loop as an identifier for the Preisach graphs. For instance, for $N=2$ there are two Preisach graphs, corresponding to the main loops (1, 2) and (2, 1).\\ 
We have shown that it is straightforward to construct all Preisach graphs by considering all permutations of the down switching fields. When hysterons are allowed to interact, however, the situation changes. On one hand, there are then $2(2^N-1)$ states $U_i^{+, -}(S)$, and because of the possibility of avalanches, the ordering between all of the states must be considered. On the other hand, the state transition graph is only determined by a partial order between some of the switching fields. As a result, the number of permutations $(2(2^N-1))!$  for interacting hysterons greatly outnumbers the number of unique state transition graphs. For $N=2$, the number of permutations is $8! = 40320$ while we know the number of graphs to be only 13. For $N=3$, the number of permutations is as high as $24! \approx 6\times 10^{23}$.\\
We thus see that it is inefficient to find all graphs for an interacting system of hysterons by considering the permutations of all switching fields. Even so, we can make use of the fact that the state transition graph only depends on a partial ordering of the switching fields. Namely, we know that each graph has an underlying set of linear inequalities $U_i(S_A) > U_j(S_B)$, which we refer to as the design inequalities\cite{vhecke2021}. The solution space of the design inequalities provides the region in parameter space that leads to the given graph. In particular, if the design inequalities have no solution, then the given graph is not realizable.\\
